Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
captions
modify figure 3

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem}}
\end{figure*}

@@

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (gs.east) edge (circle2.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Digital system equivalent to ~\ref{fig:sampledsystem}. \label{fig:digsystem1}}
\end{figure}

@@

The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
A~detailed description of DSVerifier tool can be found
in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

Given a model for a plant for which to synthesize a controller, provided in
an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and
formulates a function (step B) using implementation details provided from
Steps $2$ and $3$ to calculate the parameters of the controller to be
synthesized (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
controller synthesiser (Step D).

>>>>

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system\label{fig:sampledsystem}}
\end{figure*}

@@

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (gs.east) edge (circle2.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem}\label{fig:digsystem1}}
\end{figure}

@@

The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
A~detailed description of DSVerifier tool can be found
in~\cite{IsmailBCFF15}.  Steps $1$ to $3$ are performed by the
user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

Given a model for a plant for which to synthesize a controller, provided in
an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and
formulates a function (step B) using implementation details provided from
Step $2$ and $3$ to calculate the parameters of the controller to be
synthesized (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
controller synthesiser (Step D).
